Favipiravir - data for metaanalysis

### 2021-07-02 manuscript/hmm.Rmd
Forgotten commit for FPV metaanalysis data

res_fpv <- tibble::tribble(
  ~event, ~estimate, ~se, ~`lower95`, ~`upper95`,
  "Death",  death_res$point_estimate, NA, death_res$ci_low, death_res$ci_high,
  "Oxygen", mean(log_OR_oxygen), sd(log_OR_oxygen), quantile(log_OR_oxygen, 0.025), quantile(log_OR_oxygen, 0.975),
  "Ventilated", mean(log_OR_ventilation), sd(log_OR_ventilation), quantile(log_OR_ventilation, 0.025, na.rm=TRUE), quantile(log_OR_ventilation, 0.975, na.rm=TRUE)
  )

>>>>

res_fpv <- tibble::tribble(
  ~event, ~estimate, ~se, ~`lower95`, ~`upper95`,
  "Death",  death_res$point_estimate, death_res$sd, death_res$ci_low, death_res$ci_high,
  "Oxygen", mean(log_OR_oxygen), sd(log_OR_oxygen), quantile(log_OR_oxygen, 0.025), quantile(log_OR_oxygen, 0.975),
  "Ventilated", mean(log_OR_ventilation), sd(log_OR_ventilation), quantile(log_OR_ventilation, 0.025, na.rm=TRUE), quantile(log_OR_ventilation, 0.975, na.rm=TRUE)
  )

### 2021-07-02 other_outputs/fpv_metaanalysis.Rmd
Forgotten commit for FPV metaanalysis data

```{r}
all_res <- list()
for(exposure_day in 1:6) {

@@

  all_res[[exposure_day]] <- rbind(any_marker, by_marker) %>% mutate(day = exposure_day)
}

do.call(rbind, all_res)

>>>>

```{r}
all_res <- list()
for(exposure_day in 0:6) {

@@

  all_res[[exposure_day + 1]] <- rbind(any_marker, by_marker) %>% mutate(day = exposure_day)
}

res_to_write <- do.call(rbind, all_res) %>%
  select(marker, day, group, N, at_risk, event) %>%
  arrange(marker, day)

write_csv(res_to_write, here::here("local_temp_data", "fpv_meta", "lab_events_detailed.csv"))
